The fifteen year struggle of decentralizing privacy-enhancing technology

### 2014-03-26 paper.tex
Remove commented out paragraphs
Fix indents
Move table down so it doesn't give a huge whitespace in the paper (might be a better solution)
\newpage gives ugly whitespace
Make references and footnotes clickable and add a PDF Index
Partially rewrote the part about increasing network costs as the number of hops in a cicruit increases

% Some very useful LaTeX packages include:
% (uncomment the ones you want to load, see original template for descriptions)
%\usepackage{ifpdf}
%\usepackage{cite}
%\usepackage[cmex10]{amsmath}
%\usepackage{algorithmic}
%\usepackage{array}
%\usepackage{fixltx2e}
%\usepackage{stfloats}
%\usepackage{dblfloatfix}
%\usepackage{url}
\usepackage{graphicx}
\usepackage{epstopdf}
\usepackage{longtable}
\usepackage{caption}
\usepackage{pdflscape}
\usepackage{bbding}
\usepackage{pifont}
\usepackage{wasysym}
\usepackage{amssymb}

@@

			\item The Tor network doesn't have the capacity to handle all the users that want privacy on the internet. According to the Tor Metrics project \cite{tormetricsprojectwebsite}, it takes about 6 seconds to download 1 MiB of data. Due to the fact that traffic travels over multiple Tor nodes, the total amount of transferred data in the network multiplies. This is illustrated in figure \ref{fig:hops}. By having $n$ hops, the amount of transferred traffic would be multiplied by $2(n+1)$. This means that a 1 GiB transfer, using only 1 hop, would actually cost the network 4 GiB. By increasing the amount of Onion Routing in the Tor network, the capacity is increased. Incentives such as LIRA \cite{jansen13lira} could make more users run an Onion Router, thus increasing the capacity of the network and making it faster.

@@

	\begin{landscape}

	% Zelfde volgorde als hoofdstukken
	% Deze bij hoofdstuk 5 plaatsen!!!
	% Enkel de rijen met stukjes in tekst (I2P? Salsa?)
	\begin{table}[p]
		\centering
		\include{tbl-currentsystems}
		\caption{A comparison of decentralized peer-to-peer overlay networks}
		\label{tbl:comparison}
	\end{table}

	\end{landscape}

@@

	\newpage

@@

>>>>

% Some very useful LaTeX packages include:
% (uncomment the ones you want to load, see original template for descriptions)
%\usepackage{ifpdf}
%\usepackage{cite}
%\usepackage[cmex10]{amsmath}
%\usepackage{algorithmic}
%\usepackage{array}
%\usepackage{fixltx2e}
%\usepackage{stfloats}
%\usepackage{dblfloatfix}
%\usepackage{url}
\usepackage{graphicx}
\usepackage{epstopdf}
\usepackage{longtable}
\usepackage{caption}
\usepackage{pdflscape}
\usepackage{bbding}
\usepackage{pifont}
\usepackage{wasysym}
\usepackage{amssymb}
\usepackage[bookmarks]{hyperref}

@@

			\item The Tor network doesn't have the capacity to handle all the users that want privacy on the internet. According to the Tor Metrics project \cite{tormetricsprojectwebsite}, it takes about 6 seconds to download 1 MiB of data.

			Due to the fact that traffic travels over multiple Tor nodes, the total amount of transferred data in the network multiplies. This is illustrated in figure \ref{fig:hops}. Normally, when 1 GiB is transferred over the internet, it has a network cost of 2 GiB\footnote{1 GiB upload by the sender and 1 GiB download by the receiver, or 2 GiB in total.}. By having $n$ hops, the amount of transferred traffic would be multiplied by $2(n+1)$. As Tor uses 3 hops by default, this means that a 1 GiB transfer would result in a network cost of 8 GiB. By increasing the amount of Onion Routing nodes in the Tor network, the capacity is increased. Incentives such as LIRA \cite{jansen13lira} could make more users run an Onion Router, thus increasing the capacity of the network and making it faster.

@@

@@

@@

\begin{landscape}
	% Zelfde volgorde als hoofdstukken
	% Deze bij hoofdstuk 5 plaatsen!!!
	% Enkel de rijen met stukjes in tekst (I2P? Salsa?)
	\begin{table}[p]
		\centering
		\include{tbl-currentsystems}
		\caption{A comparison of decentralized peer-to-peer overlay networks}
		\label{tbl:comparison}
	\end{table}
\end{landscape}
